A Formal Model of Checked C

### 2023-01-20 sandp23/evaluation.tex

>>>>

We modify the instrumentation on~\code{tainted} pointers to check for a valid pointer (instead of within sandbox bounds) -- this will add the same amount of checks as in sandboxing case, but the comparison values will be different.

The marked \textcolor{red}{red} set of bars in~\fig{fig:runtimeoverhead} shows the runtime overhead. The overhead is negligible in all cases.
This shows that~\systemname{} fundamentally has the least overhead.
